\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-05 manuscript/main.tex
update teh change

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Offline Store Expansion and Platform Consolidation: Evidence from major cities in China \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation. By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network. Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores on housing transactions. Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and online platform consolidation on transaction properties. This analysis leverages the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the COVID-19 pandemic. However, this effect diminishes during the pandemic due to remote work and restrictive policies implemented by the Chinese government. The study also examines the online platform consolidation effect by analyzing the period in 2018 when Lianjia revised and improved its Agent Cooperation Network (ACN).

    \textbf{The results indicate that this strategy significantly boosts revenues and also suggest that the offline store's effect is majorly focused on people's transaction behaviors but the online platform's effect can be more insightful to provide a more efficient transaction process. } % this need to be revised.

    This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
  \end{abstract}

  \textbf{Keyword}: Marketing Strategy, Digital Platforms, Platform Consolidation, Real Estate Brokerage

@@

To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages. The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store. Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community. In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the visiting cost. Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues. At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.

@@

% need to refine
This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods. The average effect of the network is [] and the standard deviation is []. This connection is in line with the reality in several ways. Firstly, cooperation between stores to complete a transaction is very common, and having more stores within the segmented market can contribute significantly to the transaction process as more efforts can be jointly made by different agents. The collaboration between agents enhances the efficiency and effectiveness of the transaction process, leading to potentially quicker sales and better matching between buyers and properties. Secondly, the influence of the network decays with distance from subconnected nodes. This is due to the diminishing benefits of connecting with more distant nodes, as the value of information decreases with increasing distance. Information shared over longer distances may lose relevance or accuracy, thereby reducing its appeal and utility in facilitating transactions. Thirdly, we disregard each neighborhood's influence from other neighborhoods. This assumption is consistent with the observation that most houses within a neighborhood share similar characteristics, and the transaction effects within one neighborhood do not significantly impact other neighborhoods. Lastly, following Lianjia's platform consolidation strategy, the company decided to consolidate downstream brokerages to form larger clusters within the segmented market. This strategy primarily focuses on enhancing the connectivity and collaboration among stores within the network. To assess the impact of this strategy, we can examine the effects at the neighborhood level, as the increased cooperation among stores is expected to influence local market dynamics. By analyzing the neighborhood-level effects, we can better understand how the consolidation of brokerages translates into improved transaction efficiency and enhanced network effects, thereby reflecting the overall success of the platform consolidation strategy.

@@

\section{Conclusion and Discussion} \label{sec:conclusion}

In the China's real estate market the

The Chinese real estate market witnessed a significant drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.

>>>>

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Platform-Mediated Consolidation and Offline Store Expansion: Evidence from Real Estate Brokerages in Major Chinese Cities \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

@@

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform-mediated consolidation. By analyzing micro-level transactions of second-hand houses from Lianjia in ten major Chinese cities from 2016 to 2022, this research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards platform-mediated consolidation, thereby facilitating the development of an extensive franchise network. Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions. Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-based consolidation on transaction properties. The results indicate that this strategy significantly boosts revenues and attracts more people to housing tours. The results also suggest that neither the platform-based strategy nor offline expansion affects the transaction period, but offline store expansion can indeed reduce the price gap between sellers and buyers. Additionally, we proposed a measure of the network effect and found that Lianjia's offline stores show a local clustering pattern with moderate network strength. We then analyzed the effect of platform-mediated consolidation on network strength and concluded that the effect is significantly positive. This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
  \end{abstract}

  \textbf{Keyword}: Marketing Strategy, Platforms, Platform-Mediated Consolidation, Real Estate Brokerage

@@

To determine the optimal radius of influence, this research employs a regression discontinuity (RD) design on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages. The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store. Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community. In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the visiting cost. Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues. At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.

@@

% need to refine
This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods. The average effect of the network is 2.18 and the standard deviation is 2.55. This connection is in line with the reality in several ways. Firstly, cooperation between stores to complete a transaction is very common, and having more stores within the segmented market can contribute significantly to the transaction process as more efforts can be jointly made by different agents. The collaboration between agents enhances the efficiency and effectiveness of the transaction process, leading to potentially quicker sales and better matching between buyers and properties. Secondly, the influence of the network decays with distance from subconnected nodes. This is due to the diminishing benefits of connecting with more distant nodes, as the value of information decreases with increasing distance. Information shared over longer distances may lose relevance or accuracy, thereby reducing its appeal and utility in facilitating transactions. Thirdly, we disregard each neighborhood's influence from other neighborhoods. This assumption is consistent with the observation that most houses within a neighborhood share similar characteristics, and the transaction effects within one neighborhood do not significantly impact other neighborhoods. Lastly, following Lianjia's platform consolidation strategy, the company decided to consolidate downstream brokerages to form larger clusters within the segmented market. This strategy primarily focuses on enhancing the connectivity and collaboration among stores within the network. To assess the impact of this strategy, we can examine the effects at the neighborhood level, as the increased cooperation among stores is expected to influence local market dynamics. By analyzing the neighborhood-level effects, we can better understand how the consolidation of brokerages translates into improved transaction efficiency and enhanced network effects, thereby reflecting the overall success of the platform consolidation strategy.

@@

\section{Discussion and Conclusion} \label{sec:conclusion}

This paper has presented that in China's real estate market, brokerages' offline stores play an critical factor in transaction. In our baseline
